Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-13 paper/sec-mva.tex
small additions to bibliography

The classification of events as arising from either signal or
background processes via the use of a multivariate analysis is a common
technique in high energy physics~\cite{Baldi:2014pta,Wardrope:2014kya}.
%
In our work we use a specific type of  MVA to
disentangle signal and background events in the $hh\to 4b$ process,
in particular we use a multi-layer feed-forward artificial neural network (ANN),
also known as a {\it perceptron}.\footnote{This type of ANNs are the same
  as those used to parametrize Parton Distribution Functions
in the NNPDF global analyses~\cite{DelDebbio:2004qj,Ball:2008by,Ball:2011mu,Ball:2010de}.}
%
The basic idea is that the ANN is trained on an input composed on
all  signal and background
events which satisfy the
cut-based analysis, allowing to identify in an automated way
which are the most relevant variables to discriminate between the two.

>>>>

The classification of events as arising from either signal or
background processes via the use of a multivariate analysis is a common
technique in high energy physics~\cite{Baldi:2014pta,Wardrope:2014kya,Chatrchyan:2013zna}.
%
In our work we use a specific type of  MVA to
disentangle signal and background events in the $hh\to 4b$ process,
in particular we use a multi-layer feed-forward artificial neural network (ANN),
also known as a {\it perceptron}.\footnote{This type of ANNs are the same
  as those used to parametrize Parton Distribution Functions
in the NNPDF global analyses~\cite{DelDebbio:2004qj,Ball:2008by,Ball:2011mu,Ball:2010de}.}
%
The basic idea is that the ANN is trained on an input composed on
all  signal and background
events which satisfy the
cut-based analysis, allowing to identify in an automated way
which are the most relevant variables to discriminate between the two.
